Case for Support

### 2021-11-16 application/backgroundToTheResource.tex

Our proposed enhancements will \textbf{enhance, reinforce and support this key neuroinformatics
  resource to streamline reproducible experimental design, data collection and analysis, while making standardised implementations of cutting-edge machine-learning methodologies widely available to the community}, potentially creating the most powerful experimental
control and analysis tool available to neuroscientists, psychologists and
ethologists worldwide.

>>>>

The proposed project will \textbf{enhance, reinforce and support} this key neuroinformatics
resource to streamline \textbf{reproducible experimental design, data collection and analysis}, while making \textbf{standardised implementations of cutting-edge machine-learning methodologies} widely available to the community, potentially creating the most powerful experimental
control and analysis tool available to neuroscientists, psychologists and
ethologists worldwide.
